---
title: "This is an example"
author: "Sachin J Shah"
date: "2019-09-24"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

   


```{r setup, include=FALSE}

## Load the libraries we will be using
library(gapminder)
library(here)
library(socviz)
library(tidyverse)
library(plyr)

library('dplyr')      # for data manipulation
library('tidyr')      # for reshaping data

library('ggplot2')    # plotting data
library('scales')     # for scale_y_continuous(label = percent)
library('ggthemes')   # for scale_fill_few('medium')

library('ztable')     # format tables for reporting

library(data.table)
library(formattable)

knitr::opts_chunk$set(echo = FALSE) 

## Set the default size of figures
knitr::opts_chunk$set(fig.width=7, fig.height=5)  
knitr::opts_chunk$set(comment = NA)
options(ztable.type = 'html')

library(haven)
ctop_clean <- read_sas("ex_data.sas7bdat", 
    NULL)

ctop_clean <-ctop_clean[which(ctop_clean$age > 18), ]


```

###1. Use it to create updating Tables and Figures

```{r table1, echo=FALSE}

eng_tot <- sum((ctop_clean$apex_lang_cat == "1. English"))
eng_yes <- sum((ctop_clean$apex_lang_cat == "1. English") & (ctop_clean$reply_to_any_q == "Yes"))
eng_p <- eng_yes / eng_tot
eng<- prop.test(eng_yes, eng_tot)

span_tot <- sum((ctop_clean$apex_lang_cat == "2. Spanish"))
span_yes <- sum((ctop_clean$apex_lang_cat == "2. Spanish") & (ctop_clean$reply_to_any_q == "Yes"))
span_p <- span_yes / span_tot
span <- prop.test(span_yes,span_tot)

cant_tot <- sum((ctop_clean$apex_lang_cat == "3. Cantonese"))
cant_yes <- sum((ctop_clean$apex_lang_cat == "3. Cantonese") & (ctop_clean$reply_to_any_q == "Yes"))
cant_p <- cant_yes / cant_tot
cant <- prop.test(cant_yes, cant_tot)

oth_tot <- sum((ctop_clean$apex_lang_cat == "4. Other"))
oth_yes <- sum((ctop_clean$apex_lang_cat == "4. Other") & (ctop_clean$reply_to_any_q == "Yes"))
oth_p <- oth_yes / oth_tot 
oth <- prop.test(oth_yes, oth_tot)


test_table <- table(ctop_clean$apex_lang_cat, ctop_clean$reply_to_any_q)
sig_test <- chisq.test(test_table)

table1 <- data.frame(Total <- c("English", "Spanish", "Cantonese", "Other"), Respond <- c(eng_yes, span_yes, cant_yes, oth_yes), c(eng_tot, span_tot, cant_tot, oth_tot),  Percent <- c(eng_p, span_p, cant_p, oth_p))

names(table1) <- c("Language", "Responded", "Total", "Percent")

formattable(table1, align = 'r', list('Language' = formatter("span", style = ~ style(font.weight = "bold")),
            area(col = 4) ~ function(x) percent(x, digits = 0)                              
                    ))

```

###2. Use it to create updating manuscript text
In our study, we found no difference in response rate by langage. We observed a response rate of `r (round(eng[[4]],digits=2))*100`% (95% CI `r (round(eng[[6]], digits=2))*100`%) among patients who prefer English, `r (round(span[[4]],digits=2))*100`% (95% CI, `r (round(span[[6]], digits=2))*100`%) among patients who preferred Spanish, `r (round(cant[[4]],digits=2))*100`% (95% CI, `r (round(cant[[6]], digits=2))*100`%) among those who prefer Cantonese, and `r (round(oth[[4]],digits=2))*100`% (95% CI, `r (round(oth[[6]], digits=2))*100`%) among those who prefer another language (p=`r round(sig_test[[3]], digits=2)`).



